\problemname{Firetrucks Are Red}
\illustration{0.35}{numbers}{\href{https://flic.kr/p/9iKGTP}{Numbers} by Ksayer1 on Flickr, cc by-sa}%
Lily is fascinated by numbers. She believes the whole world revolves around
them, and that everything is connected by numbers. Her friends, Alice, Bob,
Charlie and Diane, are not convinced. But she gives them an example:

\begin{quote}
    Alice lives in house number 25 on her street, but that is exactly Bob's age.
    Bob is born on June 4th, and Charlie was his parents' fourth child.
    Finally, Diane has five fingers on her left hand, which happens to be the same
    as the number of toes that Bob has on his right foot!
\end{quote}

This shows that her friends are all connected---either directly or
indirectly---by numbers. But she still has to convince her family as well as
her coworkers.

Given a group of $n$ individuals, and a set of numbers that describe
each individual, help Lily come up with a proof that shows that everyone in this
group is either directly or indirectly connected by numbers, or determine that
this is not possible.

\section*{Input}
The input consists of:
\begin{itemize}
    \item One line with an integer $n$ ($2 \leq n \leq 2\cdot 10^5$), the number of
    individuals in the group. The individuals are numbered from $1$ to $n$.
    \item $n$ lines, describing the individuals in the group.

    The $i$th such line starts with an integer $m_i$ ($1 \leq m_i \leq 2\cdot
    10^5$), the number of numbers that describe individual $i$.

    The remainder of the line has $m_i$ distinct integers
    $d_{i,1},\ldots,d_{i,m_i}$ ($1 \leq d_{i,j} \leq 10^9$ for each $j$), the
    set of numbers that describe individual $i$.
\end{itemize}

It is guaranteed that the sum over all $m_i$ is at most $2\cdot 10^5$.

\section*{Output}
Output a proof in the form of $n-1$ lines, each of which contains three
integers $p$, $q$ and $r$, where $p$ and $q$ are distinct individuals
that are both described by the number $r$. Using only these relations, it
must be possible to show that any pair of individuals in the group are
connected either directly or indirectly.

If no such proof exists, output ``\texttt{impossible}''. If there are
multiple proofs, you may output any one of them.
