\begin{problem}{High Load Database}{standard input}{standard output}{2 seconds}{512 megabytes}

Henry profiles a high load database migration script. The script is the list of $n$ transactions. The $i$-th transaction consists of $a_i$ queries. Henry wants to split the script to the minimum possible number of batches, where each batch contains either one transaction or a sequence of consecutive transactions, and the total number of queries in each batch does not exceed $t$.

Unfortunately, Henry does not know the exact value of $t$ for the production database, so he is going to estimate the minimum number of batches for $q$ possible values of $t$: $t_1, t_2, \ldots, t_q$. Help Henry to calculate the number of transactions for each of them.

\InputFile
The first line contains a single integer $n$~--- the number of transactions in the migration script ($1 \le n \le 200\,000$).

The second line consists of $n$ integers $a_1, a_2, \ldots, a_n$~--- the number of queries in each transaction ($1 \le a_i$; $\sum{a_i} \le 10^6$).

The third line contains an integer $q$~--- the number of queries ($1 \le q \le 100\,000$).

The fourth line contains $q$ integers $t_1, t_2, \ldots, t_q$ ($1 \le t_i \le \sum{a_i}$).

\OutputFile
Output $q$ lines. The $i$-th line should contain the minimum possible number of batches, having at most $t_i$ queries each. If it is not possible to split the script into the batches for some $t_i$, output ``\t{Impossible}'' instead.

Remember that you may not rearrange transactions, only group consecutive transactions in a batch.

\Example

\begin{example}
\exmpfile{example.01}{example.01.a}%
\end{example}

\end{problem}

